### 2025-04-25 README.Rmd
apply suggestion from review
transition to the base pipe

To install the developmental stable version of infer, make sure to install remotes first. The `pkgdown` website for this version is at [infer.tidymodels.org](https://infer.tidymodels.org/).

@@

```{r, message = FALSE, warning = FALSE}
F_hat <- gss %>% 
  specify(age ~ partyid) %>%
  calculate(stat = "F")
```

@@

```{r, message = FALSE, warning = FALSE}
null_dist <- gss %>%
   specify(age ~ partyid) %>%
   hypothesize(null = "independence") %>%
   generate(reps = 1000, type = "permute") %>%
   calculate(stat = "F")
```

@@

```{r, message = FALSE, warning = FALSE}
null_dist %>%
  get_p_value(obs_stat = F_hat, direction = "greater")
```

>>>>

To install the developmental stable version of infer, make sure to install remotes first. The pkgdown website for this version is at [infer.tidymodels.org](https://infer.tidymodels.org/).

@@

```{r, message = FALSE, warning = FALSE}
F_hat <- gss |> 
  specify(age ~ partyid) |>
  calculate(stat = "F")
```

@@

```{r, message = FALSE, warning = FALSE}
null_dist <- gss |>
   specify(age ~ partyid) |>
   hypothesize(null = "independence") |>
   generate(reps = 1000, type = "permute") |>
   calculate(stat = "F")
```

@@

```{r, message = FALSE, warning = FALSE}
null_dist |>
  get_p_value(obs_stat = F_hat, direction = "greater")
```
